 

### 2023-05-12 paper1.Rmd
Formatting corrections

\vspace{1pt}

@@

\vspace{24pt}

@@

In addition to our base-case economic valuation, we further report our \acr{VSL} estimates using three times \acr{GDP} per capita as the value of a DALY. (Alternative valuations using values of $1,000 and $5,000, as well as \acr{PPP}-adjusted \acr{GDP} per capita, are reported in Tables S1.5 and S1.6 of Appendix 1.)

@@

Under the three approaches, we calculated the economic value of mental disorder losses (Table 1.3). `r results_sentence2`. Further adjusting for purchasing power parity, the global value of mental illness losses would exceed 7.2 trillion international dollars in 2019 (Table S1.7).

>>>>

@@

\vspace{18pt}

@@

In addition to our base-case economic valuation, we further report our \acr{VSL} estimates using three times \acr{GDP} per capita as the value of a DALY.

@@

Under the three approaches, we calculated the economic value of mental disorder losses (Table 1.3). `r results_sentence2`. Further adjusting for purchasing power parity, the global value of mental illness losses would exceed 7.2 trillion international dollars in 2019 (Table S1.7). (Alternative valuations using values of $1,000 and $5,000, as well as \acr{PPP}-adjusted \acr{GDP} per capita, are reported in Table S1.8 of Appendix 1.)

### 2023-05-12 thesis_final_version.Rmd
Formatting corrections

  # pdf_document:
  #   pandoc_args: !expr acronymsdown::add_filter()
  #   number_sections: TRUE

@@

geometry: margin=1in
fontsize: 11pt
indent: true
header-includes:
  - \usepackage{sectsty}
  - \usepackage{setspace}\spacing{2}
  - \usepackage{fancyhdr}
  - \usepackage[utf8]{inputenc}
  - \usepackage[utf8]{lscape}
  - \newcommand{\blandscape}{\begin{landscape}}
  - \newcommand{\elandscape}{\end{landscape}}
  - \usepackage[nottoc]{tocbibind}
  # - \usepackage{acro}
  # - \usepackage{float}
  # - \usepackage{chapterbib}
  # - \usepackage{lastpage}
  # - \usepackage{dcolumn}
  # - \usepackage[backend=biber,style=authoryear-icomp]{biblatex}
  # - \addbibresource{bibliography.bib}

@@

@@

`r format(Sys.time(), '%B %Y')`

@@

\vspace*{\fill}
© `r format(Sys.time(), '%Y')` Daniel Arias. All rights reserved.

@@

Dissertation Advisor: Stéphane Verguet \hfill Daniel Arias

@@

<!-- ```{r todo} -->

<!-- ### TO DO / KNOWN ISSUES -->

<!-- # Check that sequential articles are represented by a dash -->
<!-- # Institutional authors need to be fixed in bibliography -->
<!-- # Numbered figures and tables by section -->

<!-- ``` -->

>>>>

@@

geometry: margin=1in
fontsize: 11pt
indent: true
header-includes:
  - \usepackage{sectsty}
  - \usepackage{setspace}\spacing{2}
  - \usepackage{fancyhdr}
  - \usepackage[utf8]{inputenc}
  - \usepackage[utf8]{lscape}
  - \newcommand{\blandscape}{\begin{landscape}}
  - \newcommand{\elandscape}{\end{landscape}}
  - \usepackage[nottoc]{tocbibind}

@@

\addcontentsline{toc}{section}{Title page}

@@

`r format(as.Date('04-26-2023', '%m-%d-%Y'), '%B %Y')`

@@

\addcontentsline{toc}{section}{Copyright}

\vspace*{\fill}
© `r format(Sys.time(), '%Y')` Daniel Alejandro Arias. All rights reserved.

@@

Dissertation Advisor: Stéphane Verguet \hfill Daniel Alejandro Arias

@@
